---
name: Evgenii
surname: Kalenkovich
position: "Junior Research Fellow"
address: "Institute for Cognitive Neuroscience, HSE University, Moscow, Russia"
phone: +7 958 823 01 99
www: "kalenkovich.netlify.app"
email: "e.kalenkovich@gmail.com"
twitter: kalenkovich
github: kalenkovich
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
# Fixes the locale error when knitting with vitae
# From https://community.rstudio.com/t/during-startup-warning-message-setting-lc-ctype-failed-on-windows/21451/3
if (.Platform$OS.type == 'windows') {
  Sys.setlocale(category = 'LC_ALL','English_United States.1250')
} else {
  Sys.setlocale(category = 'LC_ALL','en_US.UTF-8')
}
library(vitae)
library(tibble)
library(readr)
library(glue)
```

```{r get-data}
# Education from Orcid
education.data <- rorcid::orcid_educations("0000-0002-4606-4179")$`0000-0002-4606-4179`$`affiliation-group`$summaries %>%
  dplyr::bind_rows()

# Publications from Google Scholar
# copied from https://github.com/seabbs/cv/blob/master/cv/cv.Rmd#L31-L41
pubs <- scholar::get_publications("5QzX_vUAAAAJ") %>% 
  dplyr::mutate(
    author = author %>% 
      as.character %>% 
      stringr::str_trim(),
    journal = journal %>% 
      replace(journal %in% "bioRxiv", "BioRxiv"), 
    first_author = dplyr::case_when(
      stringr::str_starts(author, "E Kalenkovich") ~ TRUE,
      TRUE ~ FALSE),
    preprint = dplyr::case_when(
      journal %in% c("bioRxiv", "BioRxiv") ~ TRUE,
      TRUE ~ FALSE)) %>% 
  dplyr::arrange(desc(year))

jobs.academic <- read_csv(
  here::here('data', 'jobs_academic.csv'),
  col_types = cols(.default = "c"))
```

# About me

I am an informal pre-doc at the Institute for Cogntive Neuroscience at HSE University.
Currently, I am running an MEG project studying syntax processing and a mousetracking project studying processing of negated sentences.
In my spare time, I am involved in several other mini-projects: a study on the role of phonemes in speech perception, development of a Python package to analyze frequency-tagging data, unsupervised classification of MEG data from the BIOMAG 2021 competition.
I do my current best to work with computational reproducibility and open science practices in mind.
Here and there I make small contributions to scientific open-source projects.

# Education

```{r show-education}
education.data %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = glue::glue("{`education-summary.organization.name`}, 
      {`education-summary.department-name`}"),
    where = `education-summary.organization.address.city`
  )
```

# Publications

```{r show-all-pubs}
pubs %>% 
  detailed_entries(
    what = title,
    when = as.character(year),
    with = author,
    where = journal, 
    .protect = TRUE
  )
```
# Experience

## Academic jobs

```{r jobs-academic}
jobs.academic %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    with = company,
    where = where,
    why = details)
```
